### 2013-08-21 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding relative flux comparison for spn verification

For the verification calculations, all solvers will be preconditioned
with ILUT using a drop tolerance of \sn{1}{-5} and a fill level of
5. For GMRES, no restrictions were placed on the size of the subspace
and therefore no restarts occurred. When the collision estimator was
used with MCSA, \sn{2}{4} stochastic histories were used to compute
the correction for every energy group in the problem (\sn{4}{4} and
\sn{8}{4} histories total for the 2 and 4 group calculations
respectively) corresponding to approximately 1 stochastic history per
DOF. When the expected value estimator was used, \sn{5}{2} stochastic
histories used for each energy group (\sn{1}{3} and \sn{1.5}{3}
histories total for the 2 and 4 group calculations) giving
approximately 1 stochastic history for every 5 DOFs. The reduced
domain approximation was also applied in conjunction with the ILUT
preconditioning using a fill level of 100 and a threshold value of
\sn{1}{-10} to reduce the density of states in the Monte Carlo
problem. For relaxation parameters, all MCSA computations used a
Neumann relaxation parameter of 0.7 while a Richardson relaxation of
1.1 was used with the collision estimator and 1.0 with the expected
value estimator as determined by the previous analysis of the
relaxation parameters. Table~\ref{tab:spn_solver_defs} gives
definitions for the solvers used to generate the results in the
remainder of this section. For the energy group structures,
Table~\ref{tab:spn_group_structure} gives the lower bounds of each
group in eV (an implicit upper bound of \sn{2}{6} eV is assumed for
group 0).
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ll}\hline\hline
      \multicolumn{1}{l}{\textbf{Name}} & 
      \multicolumn{1}{l}{\textbf{Definition}} \\
      BiCGStab-ILUT & BiCGStab preconditioned with ILUT \\
      GMRES-ILUT & GMRES preconditioned with ILUT \\
      MCSA-ILUT-R-C & MCSA preconditioned with ILUT using Richardson \\ 
                    & fixed point iteration and collision estimator \\
      MCSA-ILUT-MR-C & MCSA preconditioned with ILUT using minimal residual \\
                     & fixed point iteration and collision estimator \\
      MCSA-ILUT-R-EV & MCSA preconditioned with ILUT using Richardson \\
                     & fixed point iteration and expected value estimator \\
      MCSA-ILUT-MR-EV & MCSA preconditioned with ILUT using minimal residual \\
                      & fixed point iteration and expected value estimator \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Solver definitions used for MCSA verification and
      performance analysis.} \textit{The ILUT preconditioner
      parameters were identical for all calculations and solvers.}}
  \label{tab:spn_solver_defs}
\end{table}
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cl}\hline\hline
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{l}{\textbf{Lower Bounds (eV)}} \\
      1 & \{ \sn{1}{-5} \} \\
      2 & \{ \sn{1}{-1}, \sn{1}{-5} \} \\
      4 & \{ \sn{1}{1}, \sn{1}{0}, \sn{1}{-1}, \sn{1}{-5} \} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Energy group lower bounds for the multigroup fuel
      assembly criticality problem in electron volts.} \textit{An
      implicit upper bound of \sn{2}{6} eV is assumed for group zero.}}
  \label{tab:spn_group_structure}
\end{table}

For every combination of energy group structure and solver, the
eigenvalue problem was converged with an eigensolver tolerance of
\sn{1}{-6} and a linear solver tolerance of \sn{1}{-8} in a serial
calculation. Table~\ref{tab:serial_ev_results} gives the eigenvalue
computed by each solver for each problem as well as the number of
eigenvalue iterations required to converge. For every problem, each
solver converged to the same eigenvalue within the tolerance of the
eigensolver in the same number of eigenvalue iterations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{c}{\textbf{Iterations}} &
      \multicolumn{1}{c}{\textbf{Eigenvalue}} \\
      \hline
      BiCGStab-ILUT & 1 & 25 & 1.105987 \\
      GMRES-ILUT & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-EV & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-EV & 1 & 25 & 1.105987 \\
      \hline
      BiCGStab-ILUT & 2 & 35 & 1.155239 \\
      GMRES-ILUT & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-EV & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-EV & 2 & 35 & 1.155239 \\
      \hline
      BiCGStab-ILUT & 4 & 31 & 1.175850 \\
      GMRES-ILUT & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-EV & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-EV & 4 & 31 & 1.175850 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial eigensolver verification results for the
      fuel assembly problem.} \textit{Each calculation was converged
      with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_ev_results}
\end{table}

For each converged eigenvalue calculation, the scalar flux in each
energy group was compared over the entire spatial domain with the
BiCGStab-ILUT solution used as the reference to compute an absolute
difference of the flux in each mesh cell. For the 1 group
calculations, these absolute differences are plotted spatially along
the center-line of the fuel assembly in
Figure~\ref{fig:serial_1_group_diff}. Interestingly, except for the
MCSA-ILUT-MR-C calculation, all other 1-group calculations including
GMRES had a maximum global flux difference of \sn{9.313}{-10} even
though different spatial results were observed for all cases. For the
MCSA-ILUT-MR-C calculation, a slightly larger maximum error of
\sn{2.205}{-9} was observed for reasons that remain unexplained. All
1-group calculations have a minimum observed absolute difference of 0
with respect to the BiCGStab calculation.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/serial_1_group.pdf}
  \end{center}
  \caption{\textbf{Absolute difference of the group 0 scalar flux
      between the Aztec BiCGStab calculations and Aztec GMRES and the
      MCSA variations for the 1-group fuel assembly criticality
      calculation.} \textit{Left to right: GMRES-ILUT, MCSA-ILUT-R-C,
      MCSA-ILUT-MR-C, MCSA-ILUT-R-EV, MCSA-ILUT-MR-EV. The fluxes are
      plotted on a plane intersecting the center-line of the
      assembly. Table~\ref{tab:spn_solver_defs} gives the description
      for each solver type presented.}}
  \label{fig:serial_1_group_diff}
\end{figure}

Table~\ref{tab:serial_differences_g1},
Table~\ref{tab:serial_differences_g2}, and
Table~\ref{tab:serial_differences_g4} give the maximum and minimum
absolute differences of the cell scalar fluxes for all calculations
and all energy groups using the BiCGStab calculation as the
reference. All comparisons were performed within a group such that the
differences for the MCSA-ILUT-R-C results in group 3 for the 4-group
calculation were computed with the BiCGStab-ILUT solution in group 3
for the 4-group calculation as a reference. For all group flux results
given in the table, the maximum differences for all cases was less
than the linear solver tolerance used to converge the flux at each
eigenvalue iteration meaning that all values over the entire energy
and spatial domain are within these limits. In addition, the minimum
error for all calculations was observed to be zero, meaning that at
least one mesh cell in all calculations for all energy groups the
scalar flux values computed by all solvers were identical. Based on
the flux results and the eigenvalue results presented here, the MCSA
results should be deemed correct for the fuel assembly problem for
serial calculations with multiple energy groups.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{2.205}{-9} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{The maximum and minimum
      absolute differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{2.794}{-9} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{9.313}{-10} \\
      \hline
      GMRES-ILUT & 1 & 0.0 & \sn{4.657}{-10} \\
      MCSA-ILUT-R-C & 1 & 0.0 & \sn{1.364}{-10} \\
      MCSA-ILUT-MR-C & 1 & 0.0 & \sn{1.261}{-9} \\
      MCSA-ILUT-R-EV & 1 & 0.0 & \sn{2.474}{-10} \\
      MCSA-ILUT-MR-EV & 1 & 0.0 & \sn{5.857}{-10} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{The maximum and minimum
      absolute differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{9.313}{-10} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{1.397}{-9} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{1.870}{-9} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{1.397}{-9} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{1.869}{-9} \\
      \hline
      GMRES-ILUT & 1 & 0.0 & \sn{5.821}{-11} \\
      MCSA-ILUT-R-C & 1 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-MR-C & 1 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-R-EV & 1 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-MR-EV & 1 & 0.0 & \sn{1.164}{-10} \\
      \hline
      GMRES-ILUT & 2 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-R-C & 2 & 0.0 & \sn{2.328}{-10} \\
      MCSA-ILUT-MR-C & 2 & 0.0 & \sn{2.328}{-10} \\
      MCSA-ILUT-R-EV & 2 & 0.0 & \sn{2.328}{-10} \\
      MCSA-ILUT-MR-EV & 2 & 0.0 & \sn{2.328}{-10} \\
      \hline
      GMRES-ILUT & 3 & 0.0 & \sn{1.164}{-10} \\
      MCSA-ILUT-R-C & 3 & 0.0 & \sn{1.746}{-10} \\
      MCSA-ILUT-MR-C & 3 & 0.0 & \sn{2.256}{-9} \\
      MCSA-ILUT-R-EV & 3 & 0.0 & \sn{2.801}{-10} \\
      MCSA-ILUT-MR-EV & 3 & 0.0 & \sn{2.256}{-10} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{The maximum and minimum
      absolute differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g4}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{l}{Solver}&
      \multicolumn{1}{c}{1 Group}&
      \multicolumn{1}{c}{2 Groups}&
      \multicolumn{1}{c}{4 Groups}\\
      \hline
      BiCGStab-ILUT & 11.6 & 11.6 & 12.4 \\ 
      GMRES-ILUT & 18.1 & 17.9 & 18.9 \\
      MCSA-ILUT-R-C & 14.6 & 15.4 & 17.6 \\
      MCSA-ILUT-MR-C & 16.0 & 17.1 & 23.7 \\
      MCSA-ILUT-R-EV & 18.3 & 19.4 & 16.8 \\
      MCSA-ILUT-MR-EV & 19.6 & 22.4 & 17.5 \\
      Richardson-ILUT & 60.9 & 60.4 & 63.4 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Average number of linear solver iterations
      iterations required to converge the fixed source $SP_N$ problem
      at each eigenvalue iteration for the fuel assembly problem for
      1, 2 and 4 energy groups.} \textit{Values are rounded to the
      first decimal place. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented and Richardson-ILUT
      is a ILUT preconditioned Richardson iteration.}}
  \label{tab:spn_comparison_iterations}
\end{table}

>>>>

For the verification calculations, all solvers will be preconditioned
with ILUT using a drop tolerance of \sn{1}{-5} and a fill level of
5. For GMRES, no restrictions were placed on the size of the subspace
and therefore no restarts occurred. When the collision estimator was
used with MCSA, \sn{2}{4} stochastic histories were used to compute
the correction for every energy group in the problem (\sn{4}{4} and
\sn{8}{4} histories total for the 2 and 4 group calculations
respectively) corresponding to approximately 1 stochastic history per
DOF. When the expected value estimator was used, \sn{5}{2} stochastic
histories used for each energy group (\sn{1}{3} and \sn{1.5}{3}
histories total for the 2 and 4 group calculations) giving
approximately 1 stochastic history for every 5 DOFs. The reduced
domain approximation was also applied in conjunction with the ILUT
preconditioning using a fill level of 100 and a threshold value of
\sn{1}{-10} to reduce the density of states in the Monte Carlo
problem. For relaxation parameters, all MCSA computations used a
Neumann relaxation parameter of 0.7 while a Richardson relaxation of
1.1 was used with the collision estimator and 1.0 with the expected
value estimator as determined by the previous analysis of the
relaxation parameters. Table~\ref{tab:spn_solver_defs} gives
definitions for the solvers used to generate the results in the
remainder of this section. For the energy group structures,
Table~\ref{tab:spn_group_structure} gives the lower bounds of each
group in eV (an implicit upper bound of \sn{2}{6} eV is assumed for
group 0).
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{ll}\hline\hline
      \multicolumn{1}{l}{\textbf{Name}} & 
      \multicolumn{1}{l}{\textbf{Definition}} \\
      BiCGStab-ILUT & BiCGStab preconditioned with ILUT \\
      GMRES-ILUT & GMRES preconditioned with ILUT \\
      MCSA-ILUT-R-C & MCSA preconditioned with ILUT using Richardson \\ 
                    & fixed point iteration and collision estimator \\
      MCSA-ILUT-MR-C & MCSA preconditioned with ILUT using minimal residual \\
                     & fixed point iteration and collision estimator \\
      MCSA-ILUT-R-EV & MCSA preconditioned with ILUT using Richardson \\
                     & fixed point iteration and expected value estimator \\
      MCSA-ILUT-MR-EV & MCSA preconditioned with ILUT using minimal residual \\
                      & fixed point iteration and expected value estimator \\
      Richardson-ILUT & Richardson iteration preconditioned with ILUT \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Solver definitions used for MCSA verification and
      performance analysis.} \textit{The ILUT preconditioner
      parameters were identical for all calculations and solvers.}}
  \label{tab:spn_solver_defs}
\end{table}
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{cl}\hline\hline
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{l}{\textbf{Lower Bounds (eV)}} \\
      1 & \{ \sn{1}{-5} \} \\
      2 & \{ \sn{1}{-1}, \sn{1}{-5} \} \\
      4 & \{ \sn{1}{1}, \sn{1}{0}, \sn{1}{-1}, \sn{1}{-5} \} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Energy group lower bounds for the multigroup fuel
      assembly criticality problem in electron volts.} \textit{An
      implicit upper bound of \sn{2}{6} eV is assumed for group zero.}}
  \label{tab:spn_group_structure}
\end{table}

For every combination of energy group structure and solver, the
eigenvalue problem was converged with an eigensolver tolerance of
\sn{1}{-6} and a linear solver tolerance of \sn{1}{-8} in a serial
calculation. Table~\ref{tab:serial_ev_results} gives the eigenvalue
computed by each solver for each problem as well as the number of
eigenvalue iterations required to converge. For every problem, each
solver converged to the same eigenvalue within the tolerance of the
eigensolver in the same number of eigenvalue iterations.
\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Number of Groups}} & 
      \multicolumn{1}{c}{\textbf{Iterations}} &
      \multicolumn{1}{c}{\textbf{Eigenvalue}} \\
      \hline
      BiCGStab-ILUT & 1 & 25 & 1.105987 \\
      GMRES-ILUT & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-C & 1 & 25 & 1.105987 \\
      MCSA-ILUT-R-EV & 1 & 25 & 1.105987 \\
      MCSA-ILUT-MR-EV & 1 & 25 & 1.105987 \\
      Richardson-ILUT & 1 & 25 & 1.105987 \\
      \hline
      BiCGStab-ILUT & 2 & 35 & 1.155239 \\
      GMRES-ILUT & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-C & 2 & 35 & 1.155239 \\
      MCSA-ILUT-R-EV & 2 & 35 & 1.155239 \\
      MCSA-ILUT-MR-EV & 2 & 35 & 1.155239 \\
      Richardson-ILUT & 2 & 35 & 1.155239 \\
      \hline
      BiCGStab-ILUT & 4 & 31 & 1.175850 \\
      GMRES-ILUT & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-C & 4 & 31 & 1.175850 \\
      MCSA-ILUT-R-EV & 4 & 31 & 1.175850 \\
      MCSA-ILUT-MR-EV & 4 & 31 & 1.175850 \\
      Richardson-ILUT & 4 & 31 & 1.175850 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial eigensolver verification results for the
      fuel assembly problem.} \textit{Each calculation was converged
      with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_ev_results}
\end{table}

For each converged eigenvalue calculation, the scalar flux in each
energy group was compared over the entire spatial domain with the
BiCGStab-ILUT solution used as the reference to compute an relative
difference of the flux in each mesh cell. For the 1 group
calculations, these relative differences are plotted spatially along
the center-line of the fuel assembly in
Figure~\ref{fig:serial_1_group_diff}. Interestingly, except for the
MCSA-ILUT-MR-C calculation, all other 1-group calculations including
GMRES had a maximum global flux difference of \sn{9.313}{-10} even
though different spatial results were observed for all cases. For the
MCSA-ILUT-MR-C calculation, a slightly larger maximum relative
difference of \sn{2.205}{-9} was observed for reasons that remain
unexplained. All 1-group calculations have a minimum observed relative
difference of 0 with respect to the BiCGStab calculation.

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/serial_1_group.pdf}
  \end{center}
  \caption{\textbf{Relative difference of the group 0 scalar flux
      between the Aztec BiCGStab calculations, Aztec GMRES, Richardson
      iteration, and the MCSA variations for the 1-group fuel assembly
      criticality calculation.} \textit{Left to right: GMRES-ILUT,
      MCSA-ILUT-R-C, MCSA-ILUT-MR-C, MCSA-ILUT-R-EV,
      MCSA-ILUT-MR-EV. The fluxes are plotted on a plane intersecting
      the center-line of the assembly. Table~\ref{tab:spn_solver_defs}
      gives the description for each solver type presented.}}
  \label{fig:serial_1_group_diff}
\end{figure}

Table~\ref{tab:serial_differences_g1},
Table~\ref{tab:serial_differences_g2}, and
Table~\ref{tab:serial_differences_g4} give the maximum and minimum
relative differences of the cell scalar fluxes for all calculations
and all energy groups using the BiCGStab calculation as the
reference. All comparisons were performed within a group such that the
differences for the MCSA-ILUT-R-C results in group 3 for the 4-group
calculation were computed with the BiCGStab-ILUT solution in group 3
for the 4-group calculation as a reference. For all group flux results
given in the table, the maximum differences for all cases was less
than the linear solver tolerance used to converge the flux at each
eigenvalue iteration meaning that all values over the entire energy
and spatial domain are within these limits. In addition, the minimum
relative difference for all calculations was observed to be zero,
meaning that at least one mesh cell in all calculations for all energy
groups the scalar flux values computed by all solvers were
identical. Based on the flux results and the eigenvalue results
presented here, the MCSA results should be deemed correct for the fuel
assembly problem for serial calculations with multiple energy groups.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{4.562}{-6} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{2.099}{-5} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{4.812}{-5} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{2.371}{-5} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{3.605}{-5} \\
      Richardson-ILUT & 0 & 0.0 & \sn{1.531}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      1-group fuel assembly problem.} \textit{The maximum and minimum
      relative differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g1}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{7.590}{-6} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{5.308}{-6} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{6.387}{-5} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{4.197}{-5} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{2.736}{-5} \\
      Richardson-ILUT & 0 & 0.0 & \sn{3.976}{-6} \\
      \hline
      GMRES-ILUT & 1 & 0.0 & \sn{7.579}{-6} \\
      MCSA-ILUT-R-C & 1 & 0.0 & \sn{1.645}{-5} \\
      MCSA-ILUT-MR-C & 1 & 0.0 & \sn{2.634}{-4} \\
      MCSA-ILUT-R-EV & 1 & 0.0 & \sn{1.797}{-4} \\
      MCSA-ILUT-MR-EV & 1 & 0.0 & \sn{1.556}{-4} \\
      Richardson-ILUT & 1 & 0.0 & \sn{4.031}{-6} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      2-group fuel assembly problem.} \textit{The maximum and minimum
      relative differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g2}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{c}{\textbf{Solver}} & 
      \multicolumn{1}{c}{\textbf{Group}} &
      \multicolumn{1}{c}{\textbf{Minimum Difference}} &
      \multicolumn{1}{c}{\textbf{Maximum Difference}} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{2.376}{-5} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{2.639}{-5} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{3.958}{-5} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{2.749}{-5} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{2.969}{-5} \\
      Richardson-ILUT & 0 & 0.0 & \sn{2.189}{-5} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{2.271}{-5} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{3.702}{-5} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{3.803}{-5} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{4.142}{-5} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{2.723}{-5} \\
      Richardson-ILUT & 0 & 0.0 & \sn{2.137}{-5} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{2.310}{-5} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{2.490}{-5} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{2.214}{-5} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{4.456}{-5} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{3.366}{-5} \\
      Richardson-ILUT & 0 & 0.0 & \sn{2.143}{-5} \\
      \hline
      GMRES-ILUT & 0 & 0.0 & \sn{2.335}{-5} \\
      MCSA-ILUT-R-C & 0 & 0.0 & \sn{3.045}{-5} \\
      MCSA-ILUT-MR-C & 0 & 0.0 & \sn{2.696}{-5} \\
      MCSA-ILUT-R-EV & 0 & 0.0 & \sn{1.946}{-4} \\
      MCSA-ILUT-MR-EV & 0 & 0.0 & \sn{3.295}{-5} \\
      Richardson-ILUT & 0 & 0.0 & \sn{2.161}{-5} \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Serial scalar flux verification results for the
      4-group fuel assembly problem.} \textit{The maximum and minimum
      relative differences over the entire spatial domain are
      presented with BiCGStab used as the reference. Each calculation
      was converged with the same eigensolver and linear solver
      tolerances. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:serial_differences_g4}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccc}\hline\hline
      \multicolumn{1}{l}{Solver}&
      \multicolumn{1}{c}{1 Group}&
      \multicolumn{1}{c}{2 Groups}&
      \multicolumn{1}{c}{4 Groups}\\
      \hline
      BiCGStab-ILUT & 11.6 & 11.6 & 12.4 \\ 
      GMRES-ILUT & 18.1 & 17.9 & 18.9 \\
      MCSA-ILUT-R-C & 14.6 & 15.4 & 17.6 \\
      MCSA-ILUT-MR-C & 16.0 & 17.1 & 23.7 \\
      MCSA-ILUT-R-EV & 18.3 & 19.4 & 16.8 \\
      MCSA-ILUT-MR-EV & 19.6 & 22.4 & 17.5 \\
      Richardson-ILUT & 60.9 & 60.4 & 63.4 \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Average number of linear solver iterations
      iterations required to converge the fixed source $SP_N$ problem
      at each eigenvalue iteration for the fuel assembly problem for
      1, 2 and 4 energy groups.} \textit{Values are rounded to the
      first decimal place. Table~\ref{tab:spn_solver_defs} gives the
      description for each solver type presented.}}
  \label{tab:spn_comparison_iterations}
\end{table}
